Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-11-04 paper/paper.tex
celloVc -> cello
nonmusicians -> non-musicians

In doing so, we assume that the perception of timbre is fully invariant to frequency transposition as well as changes in dynamics.
This assumption coincides with the commonplace definition of timbre as an autonomous parameter of musical sound.
Previous studies on real-world musical sounds have confirmed that listeners are able to ignore salient pitch differences while rating timbre similarity \cite{handel2001musicperception,marozeau2003dependency}, insofar as these differences do not exceed one octave.
Since then, another study has shown that trained musicians can identify the similarity within pairs of notes from two instruments (horn and bassoon) spanning a range of $2.5$ octaves with an accuracy of $80\%$ \cite{steele2006musicperception}.
In comparison, nonmusicians has great difficulty identifying whether two notes were produced by the same instrument or not when the notes were separated by one octave.
Thus, the influence of pitch on timbre perception appears to depend upon musical training.
With this important caveat in mind, we leave as future work the question of disentangling the effects of pitch and musical training in the modeling of auditory similarities between instrumental playing techniques.

@@

\begin{itemize}
  \item Vn: violin,
  \item Va: viola,
  \item Vc: celloVc,
  \item Cb: contrabass,
  \item Hp: concert harp,
  \item Gtr: Spanish guitar,
  \item Acc: accordion,
  \item Fl: flute,
  \item BbCl: soprano clarinet,
  \item ASax: alto saxophone,
  \item Ob: oboe,
  \item Bn: bassoon,
  \item TpC: trumpet in C,
  \item Hn: French horn,
  \item TTbn: tenor trombone,
  \item BBTb: bass tuba.
\end{itemize}

>>>>

In doing so, we assume that the perception of timbre is fully invariant to frequency transposition as well as changes in dynamics.
This assumption coincides with the commonplace definition of timbre as an autonomous parameter of musical sound.
Previous studies on real-world musical sounds have confirmed that listeners are able to ignore salient pitch differences while rating timbre similarity \cite{handel2001musicperception,marozeau2003dependency}, insofar as these differences do not exceed one octave.
Since then, another study has shown that trained musicians can identify the similarity within pairs of notes from two instruments (horn and bassoon) spanning a range of $2.5$ octaves with an accuracy of $80\%$ \cite{steele2006musicperception}.
In comparison, non-musicians has great difficulty identifying whether two notes were produced by the same instrument or not when the notes were separated by one octave.
Thus, the influence of pitch on timbre perception appears to depend upon musical training.
With this important caveat in mind, we leave as future work the question of disentangling the effects of pitch and musical training in the modeling of auditory similarities between instrumental playing techniques.

@@

\begin{itemize}
  \item Vn: violin,
  \item Va: viola,
  \item Vc: cello,
  \item Cb: contrabass,
  \item Hp: concert harp,
  \item Gtr: Spanish guitar,
  \item Acc: accordion,
  \item Fl: flute,
  \item BbCl: soprano clarinet,
  \item ASax: alto saxophone,
  \item Ob: oboe,
  \item Bn: bassoon,
  \item TpC: trumpet in C,
  \item Hn: French horn,
  \item TTbn: tenor trombone,
  \item BBTb: bass tuba.
\end{itemize}
